### 2013-09-20 pystruct/paper.tex
minor fixes
vladn comments
make hyperref much prettier!! much!! prettier!!! also fix some stuff...

The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be downloaded at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

>>>>

The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\citep{dahl2006cvxopt}.

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be found at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')
